%*******************************************************
% Acknowledgments
%*******************************************************

\begingroup
\let\clearpage\relax
\let\cleardoublepage\relax
\let\cleardoublepage\relax
\chapter*{Acknowledgments}
\pdfbookmark[1]{Acknowledgments}{acknowledgments}

First and foremost, I would like to thank my supervisor, Prof.\ Dr.\ \mySupervisor. I think it is fair to say that he is the person who taught me the most about physics. His insightful advice and expertise have been invaluable in shaping my research and helping me grow as a scholar.

I would further like to thank Felix Eschment, who not only jointly worked with me on many of the results presented in this thesis, but also shared an office with me for almost 4 years---a time I will always look back too fondly.

I also wish to express my gratitude to my other collaborators, Marco Niggetiedt and Rene Poncelet, without whom this work would not have been possible. I especially thank Marco for providing Figs.~\ref{fig:5:integration2D}, \ref{fig:5:integration3D}.

Special thanks also go to Prof.\ Dr.\ Robert Harlander who second-supervised this thesis.

Furthermore, I would like to acknowledge the funding of my position by the Deutsche Forschungsgemeinschaft (DFG) under grant 396021762-TRR 257: Particle Physics Phenomenology after the Higgs Discovery, and grant 400140256-GRK 2497: The Physics of the Heaviest Particles at the LHC. Also this work would not have been possible without the computing time provided at the NHR Center NHR4CES at RWTH Aachen University (project number p0020025). This is funded by the Federal Ministry of Education and Research, and the state governments participating on the basis of the resolutions of the GWK for national high performance computing at universities (\url{www.nhr-verein.de/unsere-partner}).

Last but not least, I would like to thank my family and my friends for their unwavering support. Your love and encouragement has helped me so much throughout my life, and I feel extremely grateful to have you in my life.

I especially, like to thank my father, to whom I dedicate this thesis. He was the role model throughout my life, and it is because of him that I found my love for physics.

\endgroup
