% !TEX encoding = UTF-8
% !TEX TS-program = pdflatex
% !TEX root = ../thesis.tex


%************************************************
\chapter{Conclusions \& Outlook}\label{chap:seven}
%************************************************
\section{Conclusions}
In this work we investigated the effect of finite bottom-quark masses on the Higgs production cross section in the gluon-gluon fusion channel. We computed the top-bottom interference contribution to the cross section at \acs{NNLO}. In our recommended setup, where the bottom-quark mass is renormalized in the \MS\ scheme and included in the \acs{PDF}s, the \acs{NNLO} correction, turned out to be tiny ($+0.02\ \mathrm{pb}$ at 13~TeV), however the scale uncertainties were reduced significantly. This marks the final cornerstone in a long list of theoretical improvements on the cross section. The theoretical uncertainty is now at the level $2\%$ of the total cross section.

We also investigated the effects of alternative renormalization schemes, both for the top- and for the bottom-quark mass. We found that the cross section is quite insensitive to the renormalization scheme of the top-quark mass. For the bottom-quark mass on the other hand, the renormalization scheme turned out to be very important, as the \acs{OS} scheme, did not show good perturbative convergence at \acs{NNLO}, whereas the \MS\ did. Nevertheless, the cross section predictions in the two renormalization schemes turned out to be compatible within a 2-$\sigma$ interval. This analysis removed the scheme ambiguity previously associated with the cross section contribution.

Additionally, we examined the impact of the applied \acs{FS}. This was particularly interesting for this process, because it altered the treatment of the bottom-quark mass whenever it was not coupled to the Higgs. Our results showed that the results in the 4 and 5\acs{FS} were compatible, thus providing empirical evidence that the treatment of the bottom-quark mass in the 5\acs{FS} is indeed justified.

Besides the total cross section, we also provided results for differential cross sections, namely for the Higgs-$p_T$ and -rapidity spectrum. Our results for the $p_T$ spectrum aligned with what was found in previous studies~\cite{Caola:2018zye,Bonciani:2022jmb}. The top-bottom interference contribution, as well as the effect of finite top-quark masses to the \acs{NNLO} Higgs rapidity distribution represented new results. The combined effect shifted the \acs{rHTL} spectrum by around $-4\%$ across the entire rapidity spectrum.

Our analysis allowed us to give well grounded recommendations for future research in this field. We finally combined our findings with other state-of-the-art computations and carefully assessed their theoretical uncertainties. The resulting prediction can be used for future experimental or phenomenological applications.

\section{Outlook}
Since the theoretical uncertainty is now dominated by scale uncertainties, and this despite the fact that the cross section has been computed at partial N${}^4$LO, it is unlikely that we will see a further significant reduction of the total theory uncertainty\footnote{Although recently, there has been some progress on the computation of the full N${}^4$LO amplitudes~\cite{Chen:2025utl}}. The only uncertainty which will probably see a reduction in the near future are \acs{MHOU} in the \acs{PDF}s. This uncertainty partly arises from the incomplete \NNNLO\ DGLAP evolution kernels, \ie\ once these have been worked out, we can see a further reduction of the error. However, it is unclear, how much the uncertainty will actually improve, as the \acs{MHOU} also include the uncertainties of the perturbative cross sections the \acs{PDF}s are matched to. Additionally, even if the uncertainty would be completely removed, the impact on the total error of the cross section is almost negligible.

The best way to make significant progress at this point, is by improving on the \acs{PDF} and $\alphas$ uncertainties. We have seen in section~\ref{subsec:4:pdf_uncertainties}, that of the \acs{PDF} uncertainty estimates of the \texttt{NNPDF} and \texttt{MSHT} collaborations are vastly different. If the small uncertainties of the \texttt{NNPDF} collaboration are to be believed, then the \acs{PDF}$ + \alphas$ uncertainty would be reduced by another factor of 2! Understanding the origin of this discrepancy could be key, not only for the Higgs production cross section, but for precision predictions in general.

The low-$p_T$ region of the top-bottom interference contribution is particularly interesting, since here the effects from finite bottom-quark masses are most noticeable. Consequently, it is the region most suited for the determination of the bottom-Yukawa coupling. The fixed order $p_T$-distribution is however only reliable above $p_T \sim 20 \ \mathrm{GeV}$. Below, large logarithms can no longer be ignored and require the resummation to all orders. The origin and resummation of the appearing logarithms is not yet well understood and more research along the lines of Ref.~\cite{Caola:2018zye, Liu:2017vkm} is needed to improve our understanding as well as the precision of the cross section in this critical region of the phase space.

In experimental searches, and measurements of Higgs boson properties, one typically considers only specific production and decay channels of the Higgs. Since the decay width of the Higgs is orders of magnitude smaller than its mass $\Gamma_H /m_H = 3 \times 10^{-5}$, one can apply the narrow width approximation (see Eq.~\eqref{eq:4:narrow_width_approximation}), such that production and decay of the Higgs boson become factorized. Our results therefore serve as a stepping stone for a more precise determination of the $pp \rightarrow H \rightarrow X$ cross sections. This will be crucial, especially in the light of the high luminosity phase of the \acs{LHC}.